---
title: "Alcohol vs Seat choice"
author: "Giselle Alvarez"
date: "SPRING 2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
require(tidyverse)
require(tigerstats)
davisdata <- read.csv(file="UCDavis.csv")
```
Our Goal is to answer this question Is there a difference between the alcohol consumed between the row
you choose to sit in??

## Now with ggplot - first select the basic data

```{r}
basicCN <- ggplot(davisdata,aes(y=alcohol,x=Seat))
```
## Now add in boxplot

```{r}
basicCN + geom_boxplot()
```
  
  
### get fancy  

```{r}
basicCN + geom_boxplot(notch=TRUE,outlier.color = "red") + stat_boxplot(geom ='errorbar') + labs(title="Fancy notch boxplot \n with 2 lines")
```
  
This Boxplot shows that the heavy drinkers are mostly in the back.  
  
## Numerical Summarys 
  
```{r}
favstats(alcohol~Seat,data=davisdata)
```  
   
People who sat in the back drink three times as much alcohol than the people who sat in the front or in the middle.
    
## Inferential Tests
  
```{r}
model1 <- aov(alcohol~Seat,data=davisdata)
summary.aov(model1)
```
  
The P value is so small that it is unlikely that the alcohol consumption is all three seats is the same.   
    
## When significant follow up with TukeyHSD  

```{r}
plot(TukeyHSD(model1))
``` 
  
The TukeyHSD Plot shows that the people in the back drink a lot more than the people in the front. It shows that the people in the middle drink less then the people in the back. The middle-front shows no evidence of difference in the average alcohol consumption. 
  
## Conclusions
  
The evidence shows that most of the people that consume alcohol tend to sit in the back of the class.   
  